%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} 

\moderncvstyle{casual} 
\moderncvcolor{blue} 

\usepackage[scale=0.78]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Trever T.} % Your first name
\familyname{Hines} % Your last name
\address{2534 CC Little Bldg}{1100 North University Ave}{Ann Arbor, MI 48109-1005}
\phone{(217) 766 4445}
\social[github]{treverhines}
\email{hinest@umich.edu}

%----------------------------------------------------------------------------------------
\begin{document}

\makecvtitle % Print the CV title
\vspace*{-1cm}
% Stuff to say
% Kalman filtering, to handle real-time data integration
% Radial Basis functions and stochastic modeling, for flexible nonparametric modeling 

\section{Education}
\cvitem{2012--present}{\textbf{PhD candidate Geophysics (certificate in Computational Engineering)}
                       \newline \textit{University of Michigan}, Ann Arbor, MI}
                       
\cvitem{2008-2012}{\textbf{BS Geology}, \textit{University of Illinois}, Urbana-Champaign, IL}

\section{Doctoral Dissertation}
\cvitem{Title}{Transient deformation in tectonically active regions and implications for viscoelasticity in the crust and upper mantle}

\cvitem{Advisor}{Eric Hetland}

\cvitem{Description}{\begin{itemize}
                     \item Developed algorithms to detect spatially and temporally coherent features in 
                           large geodetic data sets
                     \item Introduced novel techniques to infer the geophysical processes causing observable 
                           ground deformation          
                     \end{itemize}}\vspace*{-6mm}

\section{Teaching Experience}
\cvitem{2014--2016}{\textbf{Graduate student instructor}, \textit{University of Michigan}
                       \begin{itemize}
                       \item Instructed labs for a graduate level course on data analysis and 
                             inverse theory
                       \item Topics included statistical hypothesis testing, Bayesian inference, 
                             regression, cluster analysis, and Kalman filtering
                       \end{itemize}}\vspace*{-4mm}
                               
\cvitem{2015}{\textbf{Michigan Math and Science Scholars instructor}, \textit{University of Michigan}
              \begin{itemize}
              \item Co-taught a summer course for high school students on the mathematics of natural 
                    hazards
              \end{itemize}}\vspace*{-6mm}
               
\section{Proficiencies}
\cvitem{Analysis}{\begin{itemize}
                  \item Supervised machine learning with stochastic processes and radial 
                        basis functions
                  \item Kalman filtering for real-time data integration
                  \item Linear and nonlinear optimization techniques
                  \item Numerical methods for solving partial differential equations
                  \end{itemize}}\vspace*{-4mm}

\cvitem{Programming}{Python, Cython, MATLAB, R, Bash, \LaTeX}

\section{Recent Publications}
\cvitem{in progress}{Hines, T. T., and E. A. Hetland. Revealing transient strain in geodetic 
                     data with the radial basis function finite difference method}
\cvitem{2016}{Hines, T. T., and E. A. Hetland. Rheologic constraints on the upper mantle from 
              five years of postseismic deformation following the El Mayor-Cucapah earthquake. 
              \textit{J. Geophys. Res.}, 121, doi: 10.1002/2016JB013114}
\cvitem{2016}{Hines, T. T., and E. A. Hetland. Rapid and simultaneous estimation of fault slip 
              and heterogeneous lithospheric viscosity from post-seismic deformation. 
              \textit{Geophys. J. Int.}, 204, doi: 10.1093/gji/ggv477}  
            
\end{document}