%% start of file `template.tex'.
\documentclass[11pt,a4paper,sans]{moderncv}   

% moderncv themes
\moderncvstyle{casual}   
\moderncvcolor{blue}   

\usepackage[utf8]{inputenc}                    
% adjust the page margins
\usepackage[scale=0.78]{geometry}
% personal data

\firstname{Trever T.} % Your first name
\familyname{Hines} % Your last name
\address{2534 CC Little Bldg}{1100 North University Ave}{Ann Arbor, MI 48109-1005}
\phone{(217) 766 4445}
\social[github]{treverhines}
\email{hinest@umich.edu}


\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{National Oceanic and Atmospheric Administration}{WFMO Staffing Division}
\date{June 27, 2017}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
%\enclosure[Attached]{Resum\'e}
\makelettertitle

I am a graduate student in geophysics at the University of Michigan. In general, my research involves analyzing GNSS data to better understand tectonic processes. As a graduate student, I continually search for new data analysis techniques that I can apply to my research. For example, I recently became interested in machine learning, which I then used to develop a method for detecting subtle geophysical signal in GNSS data. An implementation of this method, as well as all my other data analysis software, has been made freely available at www.github.com/treverhines. I am interested in this position at NOAA because I would like to further expand my knowledge of geodetic data analysis. Ultimately, I would like a career at a federal agency, which is why I am particularly excited about this Pathways opportunity. Thank you for your consideration and I look forward to your response.

\makeletterclosing

\end{document}
